---
title: "assigment2"
format: html
---

```{r}
library(haven)
TEDS_2016 <- 
  read_stata('https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true')
```

The dataset is quite large with 1690 observations and 54 variables. Also, it has many missing values which comes from the same columns. I would probably say to delete those columns that have multiple missing values. However, it greatly depends on what we are trying to analyze.

```{r}
library(ggplot2)
ggplot(TEDS_2016, aes(x = edu, y = Tondu)) +
  geom_line() +
  labs(title = " Tondu Support by Education ",
       x = "Education", y = " Tondu Support")

```

It is important to undestand what the values for Tondu means, since they are binary- support or no suport. However, they differ from each other.

```{r}
TEDS_2016$Tondu <- factor(TEDS_2016$Tondu,
levels = 1:7,
labels = c("Unification now", "Status quo, unif. in future", "Status quo, decide later", "Status quo forever", "Status quo, indep. in future",
"Independence now", "No response"))

table(TEDS_2016$Tondu)


```
```{r}
library(ggplot2)

ggplot(TEDS_2016, aes(x = Tondu)) +
  geom_bar(fill = "red") +
  labs(title = "Support for Tondu Options",
       x = "Tondu Preference",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

```

AS we have long label, I needed to change the x axis format to fit all the labels. 
